An Embedding Framework for Consistent Polyhedral Surrogates

### 2022-05-23 poly-embed-journal/poly-embed-journal.tex
Pass on conclusions

Finally, as we have
....

>>>>

Finally, while we work through applications of the framework to different target losses, we can imagine more target losses for which the embedding framework might be useful, such as multilabel learning, ranking, and (multiclass) structured prediction problems.
Understanding the application of embeddings to these settings, as well as the empirical performance of algorithms optimizing embeddings remains to demonstrate the empirical use of the framework.
